Topic modeling on EU and the USA research projects

### 2017-06-27 thesis_report/draft_thesis.tex
Add acknowledgements

>>>>

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
First of all, I would like to express my gratitude to my supervisor, Panos
Louridas. Panos provided me with invaluable advice and help throughout my MSc
thesis with his profound knowledge and a seemingly never-ending patience whilst
allowing me to work in my own way. Panos’ positive outlook and methodic approach
to solving problems has been a huge inspiration to me. He also helped me
comprehend the right research practice making these months of study a real
pleasure. Thank you.

Many thanks to my colleagues from the IST Lab. It was an honour to have a chance
to work together with such great people and brilliant researchers that helped me
broaden my research interests. I would also like to thank all of my colleagues
from the MSc in Computer Science and especially Artem Tsikiridis. I really
appreciated helpful discussions and much needed coffee breaks. Finally, I would
like to thank my family and my friends for their support and love all these
years.
\end{abstract}
